Pulling oral and IV data from CvTdb

### 2023-11-02 data-raw/Manuscript2023_Workflow.Rmd
Ensure all imports are declared and fixing some tests

@@

all_my_data %>%
  filter(Detect %in% TRUE,
         exclude %in% FALSE,
         Dose > 0) %>%
  group_by(Chemical,
           Species,
           Reference,
           Route, 
           Media,
           Dose, Time) %>%
  filter(n() > 1,
         sum(is.na(Conc)) != n(),
         LOQ < Conc) %>%
  mutate(meanConc = mean(Conc, na.rm = TRUE)) %>%
  ungroup() %>%
  rowwise() %>%
  mutate(foldConc = Conc / meanConc) %>%
  filter(Route == "iv") %>%
  count(foldConc < 0.5) %>%
  {.[[2,2]]/(.[[1,2]] + .[[2,2]])}
# Stats for ALL | ORAL | IV
# 88.64% inside twofold | 87.20%  | 91.23%
# 2.23%  above twofold  | 2.52%   | 1.70%
# 9.11%  below twofold  | 10.25%  | 7.04%

>>>>

my_coefs <- coef(my_pk) %>% inner_join(winmodel) %>% inner_join(myAIC)

my_coefs %>% dplyr::select(-sigma_value, -error_group, -coefs_vector) %>%
  ungroup() %>%
  distinct() %>%
  inner_join(other_coefs %>% dplyr::select(model, method, Chemical, Species)) ->
  my_coefs

other_coefs <- read_csv(
  "C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Figures/CvTdb_fullCoefs_20230906.csv")

other_coefs %>% dplyr::select(model, method, Chemical, Species)

write_csv(my_coefs, "C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Figures/CvTdb_fullCoefsAIC_2023.10.30.csv")

@@

all_my_data %>%
  filter(Detect %in% TRUE,
         exclude %in% FALSE,
         Dose > 0) %>%
  group_by(Chemical,
           Species,
           Reference,
           Route, 
           Media,
           Dose, Time) %>%
  filter(n() > 1,
         sum(is.na(Conc)) != n(),
         Conc > LOQ) %>% nrow()
  mutate(meanConc = mean(Conc, na.rm = TRUE)) %>%
  ungroup() %>%
  rowwise() %>%
  mutate(foldConc = Conc / meanConc) %>%
  filter(Route == "iv") %>%
  count(foldConc < 0.5) %>%
  {.[[2,2]]/(.[[1,2]] + .[[2,2]])}
# Stats for ALL | ORAL | IV
# 88.64% inside twofold | 87.20%  | 91.23%
# 2.23%  above twofold  | 2.52%   | 1.70%
# 9.11%  below twofold  | 10.25%  | 7.04%

### 2023-11-02 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Ensure all imports are declared and fixing some tests

@@

-  Change original dose units for study _S0916_ and convert to mg/kg.  
-  Change original dose units for study _S0642_ and convert to mg/kg.  
-  Include a series of isotope tracing experiments from documents _65_, _61_, _46_, and _31_.  
-  Input the LOQ for studies _S0976_ & _S0361_.  
-  Infer the LOQ for study _S0328_ as 1, given the values near it deemed above and below LOQ.  
-  Extraction from PMID:6310077 reflects a _% of Dose_, so we converted this to mg/kg.  
-  Input DTXSIDs for chemicals that did not have them but were available via CompTox dashboard.  
-  Standardize all Doses, LOQs, Concentrations, and Concentration standard deviations.  
-  Filter out chemicals dosed multiple times throughout the experiment.  
-  Filter out chemicals with very limited information.

>>>>

```{r counting-replicates}
count_query <- paste0(
  "SELECT DISTINCT ",
  "a.id, a.time_hr, a.conc, ",
  "b.id, b.analyte_dtxsid, ",
  "b.test_substance_dtxsid, b.conc_medium_normalized, ",
  "c.id, c.administration_route_normalized, ",
  "c.fk_extraction_document_id, c.dose_level_normalized, ",
  "d.id, d.species ",

query_db(query = count_query,
         schema = "cvt") %>%
  select(-id) %>% 
  filter(!is.na(analyte_dtxsid),
         analyte_dtxsid == test_substance_dtxsid,
         conc > 0) %>%
  distinct() %>%
  group_by(time_hr, analyte_dtxsid, conc_medium_normalized,
           administration_route_normalized, species, fk_extraction_document_id,
           dose_level_normalized) %>%
  count() %>%
  pull(n) %>% table()
```

@@

-  Change original dose units for study _S0916_ and convert to mg/kg.  
-  Change original dose units for study _S0624_ and convert to mg/kg.  
-  Include a series of isotope tracing experiments from documents _65_, _61_, _46_, and _31_.  
-  Input the LOQ for studies _S0976_ & _S0361_.  
-  Infer the LOQ for study _S0328_ as 1, given the values near it deemed above and below LOQ.  
-  Extraction from PMID:6310077 reflects a _% of Dose_, so we converted this to mg/kg.  
-  Input DTXSIDs for chemicals that did not have them but were available via CompTox dashboard.  
-  Standardize all Doses, LOQs, Concentrations, and Concentration standard deviations.  
-  Filter out chemicals dosed multiple times throughout the experiment.  
-  Filter out chemicals with very limited information.
